---
title: "DATA 608 HW1"
author: "Ahsanul Choudhury"
date: "September 10, 2017"
output:
  html_document:
     theme: cerulean
     toc: true
     toc_float:
       collapsed: false
       smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Load Libraries


```{r Load_libraries, echo=TRUE, results=FALSE, warning=FALSE,}
suppressMessages(if (!require('dplyr')) install.packages('dplyr'))
suppressMessages(if (!require('ggplot2')) install.packages('ggplot2'))
```

###Load Data

```{r Load_data, echo=TRUE}
data <- read.csv("https://raw.githubusercontent.com/charleyferrari/CUNY_DATA608/master/lecture1/Data/inc5000_data.csv")
```


###Graph 1

Create a graph that shows the distribution of companies in the dataset by State (ie how many are in each state). There are a lot of States, so consider which axis you should use assuming I am using a 'portrait' oriented screen (ie taller than wide).


```{r chart_1, echo=TRUE}
dplyr::count(data, State)  %>%
  mutate(State = factor(State, State)) %>%
  ggplot(aes(x = reorder(State, n), y = n))+ geom_bar(stat = "identity", width=0.5, position = position_dodge(width=0.5)) + 
  labs(title="Fastest Growing 5000 Companies: Distribution By State", x= "State", y = "Numbers") + coord_flip()
```

###Graph 2

Let's dig in on the State with the 3rd most companies in the data set. Imagine you work for the state and are interested in how many people are employed by
companies in different industries employ. Create a plot of average employment by industry for companies in this state (only use cases with full data (user R's
complete.cases() function). Your graph should show how variable the ranges are, and exclude outliers.

```{r chart_2, echo=TRUE}
dNY <- data[complete.cases(data), ]
dNY <- subset(data, State == "NY") 


dNY <- group_by(dNY, Industry) %>% summarize(m = mean(Employees), max= max(Employees), min = min(Employees)) %>%
  na.omit()

upper <- dNY$max
lower <- dNY$min




ggplot(dNY, aes(x = Industry, y =m, ymax=max,  ymin = min, lower = lower, upper= upper)) + geom_boxplot(outlier.shape = NA) + coord_flip()+
  labs(title="Number of Employees By Industry in NY State", y = "Mean")


```

###Graph 3

Now imagine you work for an investor and want to see which industries generate the most revenue per employee. Create a chart makes this information clear

```{r chart_3, echo=TRUE}
data_rev <- data[complete.cases(data), ] 
data_rev %>% 
  group_by(Industry) %>% 
  summarise(Total_Revenue = sum(Revenue), Total_employee = sum(Employees))%>%
  mutate(RevPerEmp = (Total_Revenue/Total_employee))%>%
ggplot(aes(x=reorder(Industry, RevPerEmp), y=RevPerEmp)) + 
    geom_bar(stat="identity", width=.5) +
    labs(title="Revenue Per Employee by Industry", x ="Industry", y = "Revenue Per Employee") + coord_flip()
```

###References:

https://stackoverflow.com/questions/11562656/average-data-by-group


